### 2021-04-19 input/figproofA.tex
preparing
reworkd figure

  \newcommand\X{70pt}
  \newcommand\Y{-40pt}

@@

  \draw[opacity=0] (-1.5*\X, 0) -- (1.5*\X, 0);

  \draw[<->] (-5pt - \X, -\Y) -- node[above]{I} (5pt, -\Y); %% I

  \draw[->] (-\X + 5pt, 0) --
  node[above, color=\PA, font=\small]{$\ADD_a^1$}
  (0 - 5pt, 0); %% a - b

  \draw[<->] (-5pt, 5pt -\Y) -- node[above]{II} (5pt + \X, 5pt -\Y); %% II
  \draw[->] (0 + 5pt, 0) -- (-5pt +  \X, 0); %% b - c

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^0$};
  \draw ( 0, 5pt) node[above, color=\WRONG]{$\ADD_d^{0.5}$};
  \draw (\X,-5pt) node[below, font=\scriptsize]{expect \textcolor{\PA}{$\alpha_a$}};
  \draw (0, -5pt) node[below, font=\scriptsize]{expect $\textcolor{\PC}{\DEL_d} \rightarrow \textcolor{\PA}{\alpha_a}$};

>>>>

  \newcommand\X{95pt}
  \newcommand\Y{-50pt}

@@

  \draw[opacity=0] (-1.2*\X, 0) -- (1.2*\X, 0);

  \draw[->] (-1.15*\X, 0) -- (-5pt + -1*\X, 0); \draw[dotted] (-1.25*\X, 0) -- (-1.15*\X, 0);
  \draw (5pt + \X, 0) -- (1.15*\X, 0); \draw[dotted,->] (1.15*\X, 0) -- (1.25*\X, 0);

  \draw[<->] (5pt - \X, 0.4*\Y) -- node[below, font=\small]{\textbf{I: propagation}} (-5pt, 0.4*\Y); %% I

  \draw[->] (-\X + 5pt, 0)
  node[below=-0.3em, below right, font=\tiny]{$\textcolor{\PA}{\ADD_a^{x'}} \rightarrow$}
  --
  (0 - 5pt, 0); %% a - b

  \draw[<->] (5pt, 0.4*\Y) -- node[below, align=center, font=\small]{\textbf{II: need purge}\\with I', III, IV} (-5pt + \X, 0.4*\Y); %% II
  \draw[->] (0 + 5pt, 0) -- (-5pt +  \X, 0); %% b - c

  \draw[fill=white] (-\X, 0) node[color=\PA]{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node[color=\PD]{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^x$};
  \draw ( 0, 5pt) node[above]{$
    \xrightarrow[\textcolor{\PD}{\ADD_d^y}]{\mbox{\small{last}}}
    \xrightarrow[\DEL_d \rightarrow \textcolor{\PA}{\ADD_a^{x'}}]{\mbox{\small{expect}}}$};

  \draw (-5pt, 0pt) node [below=-0.3em, below left, font=\tiny]{$\textcolor{\WRONG}{\ADD_d^y < \ADD_a^{x'}}$};
  % \draw (-5pt, 0pt) node [below=-0.3em, below left, font=\tiny]{$\textcolor{\WRONG}{\ADD_d^{y} < \ADD_e^z}$};

  \draw (\X, 5pt) node[above]{$
    \xrightarrow[\textcolor{\PA}{\ADD_a^{x''}}]{\mbox{\small{expect}}}$};
%  \draw (0, -5pt) node[below, font=\scriptsize]{expect $\DEL_d \rightarrow \textcolor{\PA}{\ADD_a}$};

  \draw[->] (-\X,  0.5*\Y) -- (-\X, -5pt);
  \draw[dotted] (-\X,  0.5*\Y) -- (-\X, 0.9*\Y);

  \draw[->] ( 0,  0.5*\Y) -- ( 0, -5pt);
  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y) node[below, font=\scriptsize]{somewhere: $\textcolor{\PD}{\ADD_d} \rightarrow \DEL_d$};

  \draw[->] ( \X,  0.5*\Y) -- ( \X, -5pt);
  \draw[dotted] ( \X,  0.5*\Y) -- ( \X, 0.9*\Y);

### 2021-04-19 input/figproofB.tex
reworkd figure

  \newcommand\X{85pt}
  \newcommand\Y{-40pt}

@@

  \draw[<->] (-5pt - \X, -\Y) -- node[above]{I': propagation} (5pt, -\Y); %% I as well
  \draw[->] (-\X + 5pt, 0) -- node[above, font=\small]{$\DEL_d$} (0 - 5pt, 0); %% d - e

  \draw[<->] (-5pt , 5pt -\Y) -- node[above]{III: detection} (5pt + \X, 5pt -\Y); %% IV
  \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% e - b'

  \draw[<->] (-5pt + \X , 10pt -\Y) -- node[above]{IV: propagation} (5pt + 2*\X, 10pt -\Y); %% V
  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% b - b''

  \draw[fill=white] (-\X, 0) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{b'}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (2*\X, 0) node{$\bm{b''}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above]{$\DEL_d$};

  \draw ( 0, 5pt) node[above]{$\textcolor{\PC}{\ADD_d} \rightarrow \textcolor{\WRONG}{\ADD_f^{0.5}}$};
  \draw ( 0, -5pt) node[below, font=\footnotesize]{expect $\DEL_f$};

  \draw ( \X, 5pt) node[above]{$\textcolor{\PB}{\ADD_f^1} \rightarrow \DEL_f \rightarrow \textcolor{\PC}{\ADD_d^{0.5}}$};
  \draw ( \X, -5pt) node[below, font=\footnotesize]{expect $\DEL_d$ or $\DEL_d^{0.5}$};

  \draw (2*\X, 5pt) node[above]{$\textcolor{\PC}{\ADD_d^{1.5}}$};
  \draw (2*\X, -5pt) node[below, font=\footnotesize]{expect $\DEL_d$ or $\DEL_d^{1.5}$};

>>>>

  \newcommand\X{85pt}
  \newcommand\Y{-50pt}

@@

  \draw[->] (-1.15*\X, 0) -- (-5pt + -1*\X, 0); \draw[dotted] (-1.25*\X, 0) -- (-1.15*\X, 0);
  \draw (5pt + 2*\X, 0) -- (2.15*\X, 0); \draw[dotted,->] (2.15*\X, 0) -- (2.25*\X, 0);

  \draw[<->] (5pt - \X, 0.4*\Y) --
  node[below, font=\small]{\textbf{I': propagation}}
  (-5pt, 0.4*\Y); %% I as well

  \draw[->] (-\X + 5pt, 0)
  node[below=-0.3em, below right, font=\scriptsize]{$\DEL_d \rightarrow$}
  -- (0 - 5pt, 0)
  node [below=-0.15em, below left, font=\tiny]{$\textcolor{\WRONG}{d \neq f}$}
  ; %% d - e

  \draw[<->] (5pt , 0.4*\Y) --
  node[below, font=\small]{\textbf{III: detection}}
  (-5pt + \X, 0.4*\Y); %% IV

  \draw[->] (0 +5pt, 0)
  node[below=-0.3em, below right, font=\tiny]{$\textcolor{\PF}{\ADD_f^{z'}} \rightarrow$}
  --
  (\X -5pt, 0)
  node [left= -0.15em, below=-0.3em, below left, font=\tiny]{$\textcolor{\WRONG}{\DEL_f \not\rightarrow \ADD_f^{z'}}$}
  ; %% e - b'

  \draw[<->] (5pt +\X , 0.4*\Y) --
  node[below, font=\small]{\textbf{IV: propagation}}
  (-5pt + 2*\X, 0.4*\Y); %% V

  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% b - b''

  \draw[fill=white] (-\X, 0) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node[color=\PF]{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node[color=\PD]{$\bm{b'}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (2*\X, 0) node[color=\PD]{$\bm{b''}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above]{$\textcolor{\PD}{\ADD_d} \rightarrow \DEL_d$};

  \draw ( 0, 5pt) node[above, font=\footnotesize]{$
    \xrightarrow[\textcolor{\PC}{\ADD_d^{\vphantom{z'}}}]{\mbox{\scriptsize{before}}}
    \xrightarrow[\textcolor{\PF}{\ADD_f^{z\vphantom{'}}}]{\mbox{\scriptsize{last}}}
    \xrightarrow[\DEL_f^{\vphantom{z'}} ]{\mbox{\scriptsize{expect}}}$};

  \draw ( \X, 5pt) node[above, font=\footnotesize]{$
    \xrightarrow[\textcolor{\PF}{\ADD_f^{\vphantom{y'}}} \rightarrow \DEL_f]{\mbox{\scriptsize{before}}}
    \xrightarrow[\textcolor{\PC}{\ADD_d^{y'}}]{\mbox{\scriptsize{last}}}
    \xrightarrow[\DEL_d^{\vphantom{z'}}?]{\mbox{\scriptsize{expect}}}$};

  \draw (2*\X, 5pt) node[above, font=\footnotesize]{$
    \xrightarrow[\textcolor{\PC}{\ADD_d^{y''}}]{\mbox{\scriptsize{last}}}
    \xrightarrow[\DEL_d^{\vphantom{y'}}?]{\mbox{\scriptsize{expect}}}$};

  \draw[->] (-\X,  0.5*\Y) -- (-\X, -5pt);
  \draw[dotted] (-\X,  0.5*\Y) -- (-\X, 0.9*\Y);

  \draw[->] ( 0,  0.5*\Y) -- ( 0, -5pt);
  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y) node[below right, font=\scriptsize]{somewhere: $\textcolor{\PF}{\ADD_f} \rightarrow \DEL_f$};

  \draw[->] ( \X,  0.5*\Y) -- ( \X, -5pt);
  \draw[dotted] ( \X,  0.5*\Y) -- ( \X, 0.9*\Y);

  \draw[->] (2*\X,  0.5*\Y) -- (2*\X, -5pt);
  \draw[dotted] (2*\X,  0.5*\Y) -- (2*\X, 0.9*\Y);
